Where do I begin? I am a summation of all the people that I have come in contact with throughout my life. So, I would like to dedicate this text to some of the most influential people. 

I start with my mother Patricia Lowe who always encouraged me to pursue my wildest dreams. My father William Robertson, who taught me to question the world and to always pay attention to the small things. My brother Fard Lowe, who consistently served as an inspiration to me and was someone I could always count on. To my high school counselor, Kathy Giles-Harris and high school math teacher, Christopher Reese who both saw something special in me, and pushed me to pursue it. 

My brothers from Morehouse\textemdash Terron Ferguson, Ryan Shepard, John-Marcus Philips, Sean Brazier and Kelechi Kalu\textemdash who kept the laughs and good times rolling along my journey. You guys always made me feel cool, even though I'm a science nerd.
  
My MSU family, who are too many to name, but I'll name a few\textemdash my brother and sister, Cameron Khalfani Herman and Neem Serra, my best bud Ruby Carrillo, Dr. Barbara Thelamour, my mentor Judi Brown-Clarke, my problem solvers Connie James and Darcie Zubek, Carmel Martin-Fairey, Daniel Couvrtier, Luis Zaman, Chad Byers, Temple Smith, James Kremer, okay I said a few, so I'll stop there. I needed you all along the way, through late nights of studying, endless laughs, awesome food, much needed pep talks and just being there to help me survive Michigan.

Collaborators and friends, Billie Swalla, her lab, Lionel Christiaen, his lab, Alberto Stolfi and the wonderful Princess Claudia Racioppi, who all helped me to develop as biologist, experimentally and conceptually, and who advised me along the way. I look forward to working with you all for years to come. And a special thanks to Billie without whom this project would not exist. We have traveled the world together (well at least a good part of the US and Europe), and done what I think is some good science together.

My advisor, Titus Brown. I cannot thank you enough for guiding me along the way. I truly lucked out when I landed in your lab. You are a great scientist, adviser, mentor, and person, and this is the only time you'll hear (or more like read) me say this.

My awesome committee\textemdash David Arnosti, Jin Chen, Ian Dworkin, and Yanni Sun\textemdash who were always tough, but fair.

And to those who pursue knowledge not for the sake of notability but just to make the world a better place.
