\chapter{Background}
Chordates are a branch of deuterostome that are characterized by a dorsal nervous system, pharyngeal gill slits, and defined by the presence of a notochord. Tunicates are one of the three subphyla of chordates and are grouped because of their outer covering known as a tunic. During development tunicates form a tailed larvae that closely resembles the vertebrate body plan \cite{jeffery_minireview_2002} and this tadpole larvae is typical of \textasciitilde 3000 tunicates \(cite\). Out of these 3000 species 16 are known to have independently lost their larval tail, with the majority of them being \textit{Molgula} \cite{berrill_studies_1931,swalla_interspecific_1990}. During this time, known as the free-swimming stage, the elongation and mobility of the tail is depended upon the proper formation of the notochord and muscle cells \cite{satoh_ascidian_2003}. As a tissue the notochord is closest related to cartilage and serves as the axial skeleton of the embryo in addition to a source patterning signaling \cite{jeffery_evolution_1999}. In ascidians and in lower vertebrae the improper formation of the notochord leads to severely shortened larva that cannot swim or feed properly \cite{di_gregorio_tail_2002,jiang_ascidian_2005,stemple_structure_2005}. We present a comparative study of the tailed \textit{M. oculata} and the tail-less \textit{M. occulta} through gene expression in order to understand the underlying factors behind tail development and tail loss.

Ascidians are a simpler system to study developmental processes, their development is well studied, they have invariant early cell lineages, a small number of cells \cite{lemaire_evolutionary_2011} and there has been no documentation of ascidians developing without an invariant cell lineage \cite{lemaire_ascidians_2008}. Although, this study present the first \textit{Molgula} genomes assemblied, there the assembled and annotated genome of \textit{Ciona intestinalis} which serves as a  In \textit{Ciona intestinalis} there are ~2,600 cells, 36 of them being muscle, 40 of them being notochord and many of these cells have be traced starting at fertilization. Tunicates have a small number of cells compared to vertebrates, they also have rapid embryogenesis, compact genomes, few larval tissue types, simplified larval body plans and shallow gene networks \cite{corbo_characterization_1997,jeffery_minireview_2002,dehal_draft_2002}. For all of these reasons tunicates make great models for both tail development and loss, in addition to several Molgulids independently losing their tail and two of the Molgulids, a tailed and tailless species having the ability to hybridize \cite{jeffery_evolutionary_1991}. 


Sequence technology has continued to advance and become cheaper. Technology such as Ion Torrent, Roche 454 and Illumina has made genome or transcriptome wide analysis more readily available for non-model species. These technologies have several advantages over the prior standard mircoarray; they have a wider scope, are more precise and are able for find novel genes \cite{}. 
With the advances in technology when can now sequence the transcriptomes of both species and their hybrid. This always use to look at pivotal time points in tail development and compare across closely related species. This type of study has yet to be done. Genes have been identified by both hybridization and subtractive screening (hotta, swalla, satoh, etc). 

Tail development has been previously studied in ascidians and other chordates, with no one factor being the cause of a improperly form tail or lack of tail. 

Tail development and lost has been studied on 
We started this project with the mRNA of the two Molgula species and their hybrid. mRNA was collected for three time points in all 

genes have been idenitified in C. intestinalis, holycythia rorzi using substrative methods and microarrays. In molgula a global view has yet to be examined. However, several genes have been identified, using the tailed, tail-less and the hybrid. 

We started this project with RNA-seq data which presented us with the problem of determining which assembly was the best and what metrics should be used to analysis them.

Experiemential techniques have yet to be adapted to \textit{M. occult} and \textit{M. oculata} because of there short gustation period, not being able to be cultured in lab conditions, although this is being currently developed amongst embryo specific difficulties. Most of the studies for tail development have been done in \textit{C. intestinalis} and \textit{H. roretzi}  