\chapter{Contributions}
\section{Chapeter 3: Evaluating a lightweight transcriptome assembly pipeline on two closely related ascidian species}
The experimental design for the RNA sequence analysis was decided by C. Titus Brown (CTB) and Billie J. Swalla (BJS). The fertilization and collection of RNA samples were done by BJS and myself. Library preparation for Illumina sequencing was done by Kanchan Pavangadkar. All downstream analysis was done by myself. The idea for evaluating the de novo assembly pipeline came about through conversations with CTB, as well as methods for evaluating the transcriptome assemblies. Writing was done by me with edits from BJS and CTB.

\section{Chapter 4: Genome assembly and characterization}
The experimental design for the DNA sequencing was decided by CTB, BJS, and Lionel Christiaen (LC). Embryonic samples were collected by BJS, LC, Alberto Stolfi (AS), Claudia Racioppi (CR) and myself. Genome assembly was conducted by me. Ideas for examining divegand were developed by AS, orthologous sequences were identified through the use of RBH blast and done so by me because the sequences were not yet annotated on the Aniseed database. The \textit{Hox} analysis was done by me and was initiated by a question from David Arnosti. Writing was done by AS, myself with edits from BJS, CTB, CR, and LC.

\section{Chapter 5: Differential expression analysis of tail loss in an invertebrate chordate}
The experimental design is the same for the ``Evaluating a lightweight transcriptome assembly pipeline on two closely related ascidian species'' chapter (3). Transcript models were assembled by me. Read mapping for differential expression analysis was conducted by me, and the analysis of hybrid expression counts was the idea of CTB. The differential expression analysis was conducted by me, including the idea to focus on the overlapping upregulated gene in \textit{M. oculata} and the interspecific hybrid. Annotation of the overlapping upregulated genes was done by AS, Anna Di Gregorio and myself. Writing was done by me with edits from AS, CR, and CTB.